%------------------------
% Resume Template
% Author: Anubhav Singh
% Github: https://github.com/xprilion
% License: MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome} 

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]


%---------------------------------------
%------------Custom commands------------

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSectionListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSectionListEnd}{\end{itemize}}

\newcommand{\resumeSubheading}[2]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTitle}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemWithTitle}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }\vspace{-3pt}
}

\newcommand{\resumeItemWithoutTitle}[1]{
    \item[$\bullet$]\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------
%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%

\begin{document}


%------------HEADING------------------

\begin{center}
    \textbf{{\Huge \scshape Ankith Kumar Anawal}} \\
    \vspace{1pt}
    \small +91xxxxxxxxxx $|$ \href{mailto:}{\underline{xxxx@gmail.com}} $|$ \href{https://linkedin.com/in/ankithkumar99/}{\underline{linkedin.com/in/ankithkumar99/}}
\end{center}


%------------PROFILE------------------

\section{Profile}
    \resumeSectionListStart
        \item
        Data Engineer with 3+ years of experience in big data and analytics. Experienced in building data platforms, large-scale data pipelines, ETL processes, and data warehouse solutions. Utilized technologies like \textbf{Python, SQL, Spark, Azure Cloud Services, Databricks}.
        \vspace{-5pt}
    \resumeSectionListEnd


%-----------EDUCATION-----------------

\section{Education}
    \resumeSectionListStart
        \resumeSubheading
            {Jawaharlal Nehru Technological University}{Hyderabad, IN}
            \resumeSubheadingTitle
                {Bachelor's in Computer Science and Engineering}{July 2017 -- August 2021}
    \resumeSectionListEnd 

        
%--------Technical Skills-------------

\section{Technical Skills}
    \resumeSectionListStart
        \resumeItemWithTitle{Languages}{Python, SQL, Java, YAML, C/C++, JavaScript, HTML/CSS}
        \resumeItemWithTitle{Cloud Skills}{Azure Databricks, Azure Data Factory, Azure Data Lake Storage, Azure DevOps, Salesforce CRM}
        \resumeItemWithTitle{Databases}{Azure SQL Database, MySQL, MongoDB}
        \resumeItemWithTitle{Data Engineering}{Apache Spark, Batch and Streaming processing, CICD, ETL/ELT Pipelines}
        \resumeItemWithTitle{Tools}{Git/GitHub, VSCode, Azure Repos, Azure Storage Explorer, Salesforce Inspector, Microsoft 365}
    \resumeSectionListEnd


%---------------------

\section{Experience}
    \resumeSectionListStart
        \resumeSubheading
            {Tata Consultancy Services}{Hyderabad, IN}
            \resumeSubheadingTitle
                {Azure Data Engineer -- Diageo}{November 2023 -- Present}
                \resumeItemListStart
                    \resumeItemWithoutTitle{
                        Developed and enhanced a \textbf{no-code ingestion platform} using PySpark within a \textbf{Medallion Architecture} framework, ensuring scalable and efficient data processing through bronze, silver, and gold layers.
                    }
                    \resumeItemWithoutTitle{
                        Designed and managed YAML-based configurations to automate and streamline the setup of data ingestion workflows, reducing manual intervention and enhancing the flexibility of the platform.
                    }
                    \resumeItemWithoutTitle{
                        Built and optimized \textbf{ETL pipelines} to process and transform large datasets, integrating real-time and batch processing workflows using \textbf{Azure Databricks} and \textbf{Azure Data Lake Storage}.
                    }
                    \resumeItemWithoutTitle{
                        Implemented automated data quality checks and reconciliation processes, reducing errors and improving overall data integrity.
                    }
                    \resumeItemWithoutTitle{
                        Developed a robust \textbf{PII framework}, for securely hashing sensitive data prior to processing and storing it in a secure SQL database, ensuring compliance with GDPR data protection regulations.
                    }
                    \resumeItemWithoutTitle{
                        Conducted PR reviews for new features and optimizations, ensuring adherence to coding standards, best practices, and framework guidelines.
                    }
                    \resumeItemWithoutTitle{
                        Provided support for data architecture and ingestion processes, enabling teams to leverage the data platform for business intelligence and reporting purposes.
                    }
                \resumeItemListEnd
            \resumeSubheadingTitle
                {Data Analyst -- Diageo}{August 2021 -- November 2023}
                \resumeItemListStart
                    \resumeItemWithoutTitle{
                        Worked extensively with the \textbf{Contract Management} module of \textbf{Salesforce CRM}, which is designed to streamline the creation, management, and tracking of contracts throughout their lifecycle, from creation to the renewal and expiration.
                    }
                    \resumeItemWithoutTitle{
                        Responsible for analyzing and understanding the data model of the Contract Management application, ensuring comprehensive analysis of contract-related data to support reporting and decision-making.
                    }
                    \resumeItemWithoutTitle{
                        Developed and maintained custom reports and dashboards within Salesforce using \textbf{Salesforce Reports and Lightning Components}, enabling real-time visibility into contract statuses and business performance metrics.
                    }
                    \resumeItemWithoutTitle{
                        Shared actionable insights with senior management that directly contributed to a \textbf{15\% increase in new contracts} by optimizing contract strategies and improving lead conversion.
                    }
                    \resumeItemWithoutTitle{
                        Worked with \textbf{Salesforce SOQL (Salesforce Object Query Language)} to extract, filter, and analyze contract-related data, ensuring the accuracy of the data in reports.
                    }
                    \resumeItemWithoutTitle{
                        Performed \textbf{data cleansing and transformation} tasks to ensure data quality and consistency, ensuring the accuracy of contract data in reports.
                    }
                    % \resumeItemWithoutTitle{
                    %     Provided regular updates to senior management on contract performance and proposed recommendations to improve business processes.
                    % }
                \resumeItemListEnd
        \resumeSubheading
            {Ethical Edufabrica Ltd}{Hyderabad, IN}
            \resumeSubheadingTitle
                {Internship}{February 2021 -- March 2021}
                \resumeItemListStart
                    \resumeItemWithoutTitle{
                        Gained hands-on experience in applying \textbf{supervised learning} (e.g., Linear Regression, Decision Trees, SVM) to analyze educational data. Assisted in implementing and optimizing machine learning models to predict student performance, course completion rates, and engagement levels.
                    }
                    \resumeItemWithoutTitle{
                        Collaborated with senior data scientists to conduct \textbf{exploratory data analysis (EDA)} on large educational datasets to identify trends and patterns in student behavior. Worked with \textbf{scikit-learn} to preprocess datasets, clean data, handle missing values, and engineer features for better model accuracy.
                    }
                \resumeItemListEnd
    \resumeSectionListEnd


%-----------PROJECTS-----------------

\section{Projects}
    \resumeSectionListStart
        \resumeProjectHeading{\textbf{Audio Classification} $|$ \emph{Python, Keras, TensorFlow, CNNs, MFCC, Audio Signal Processing}}{}
            \resumeItemListStart
                \resumeItemWithoutTitle{
                    Developed a deep learning model for audio classification to classify audio signals into predefined categories. Utilized \textbf{CNNs} and \textbf{Mel-frequency cepstral coefficients (MFCC)} to efficiently process and classify audio data.
                }
                \resumeItemWithoutTitle{
                    Applied \textbf{Keras} and \textbf{TensorFlow} frameworks for model training and evaluation, optimizing the model for higher accuracy. Conducted comprehensive data pre-processing including noise reduction, feature extraction, and normalization to improve classification performance.
                }
                % \resumeItemWithoutTitle{
                %     Achieved significant improvements in classification accuracy and demonstrated real-time applications in audio signal processing.
                % }
            \resumeItemListEnd
    \resumeSectionListEnd

\end{document}
